---
title: "Shiny Application and Reproducible Pitch"
author: "Satya Pechetty"
date: "November 19, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny Application
Summary

The sample shiny application uses slider generated from random numbers and Widgets included textbox, radiobutton,  checkboxgroup and text to receive from users and provide results to users. 


## The ui.R file

It uses the fluidPage layout.
Then, to ensure all the information is not crammed onto one page, the tabsetPanel has been used to effectively put multiple pages all on one page.
Radio buttons have been used instead of a select menu. This means the user can change their choices even quicker than with select boxes.


```{r Radio1, echo=FALSE ,message=FALSE}
 library(shiny)
```

## Slide with R Output
```{r Radio11, echo=TRUE ,message=FALSE}
 if (interactive()) {

ui <- fluidPage(
  sliderInput("obs", "Number of observations:",
    min = 0, max = 1000, value = 500
  ),
  plotOutput("distPlot")
)

# Server logic
server <- function(input, output) {
  output$distPlot <- renderPlot({
    hist(rnorm(input$obs))
  })
}

# Complete app with UI and server components
shinyApp(ui, server)
}
```

## Slide with R Output

The server.R file
Makes use of the renderDataTable function. This means that the results can be stored in server.R as a data frame for easy R calculation.


